FlowFPX: Nimble Tools for Debugging Floating-Point Exceptions

### 2024-07-25 paper.tex
Start work on fixing paper for submission
Fix floatmin/floatmax issue

\begin{lstlisting}[language = Julia]
julia> prevfloat(typemax(Float64))
1.7976931348623157e308
julia> nextfloat(typemin(Float64))
-1.7976931348623157e308
\end{lstlisting}

@@

\FlowFPX{} is a toolkit for tracking down \fp{} exceptions.
The primary tools in this paper are \FT{}, which records lifetimes
and enables fuzzing, and \CSTG{}s (more precisely, CSTGs), which visualize
the flow of exceptions.
\GPUFPX{} is a third component of \FlowFPX{} that tracks \fp{} exceptions inside GPU kernels~\cite{llsflg-hpdc-2023}.

@@

% Local Variables:
% jinx-local-words: "BinFPE CFL CSTG's CSTGs Courant Demmel FPChecker Friedrichs Herbie JuliaHub Klöwer Lewy OrdinaryDiffEq RxInfer ShallowWaters Sherlogs TrackedFloat isnan"
% citar-bibliography: ("./ref.bib")
% End:

>>>>

\begin{lstlisting}[language = Julia]
julia> floatmax(Float64)
1.7976931348623157e308
julia> floatmin(Float64)
2.2250738585072014e-308
\end{lstlisting}

@@

\FlowFPX{} (FPX: Floating Point eXeption) is a toolkit for tracking down \fp{} exceptions.
The primary tools in this paper are \FT{}, which records lifetimes
and enables fuzzing, and \CSTG{}s (more precisely, CSTGs), which visualize
the flow of exceptions.
\GPUFPX{} is a third component of \FlowFPX{} that tracks \fp{} exceptions inside GPU kernels~\cite{llsflg-hpdc-2023}.

@@

% Local Variables:
% jinx-local-words: "BinFPE CFL CSTG's CSTGs Courant Demmel FPChecker Friedrichs Herbie JuliaHub Klöwer Lewy OrdinaryDiffEq RxInfer ShallowWaters Sherlogs TrackedFloat isnan"
% citar-bibliography: nil
% End:
